The Astropy Project

### 2017-11-22 main.tex

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
Roughly half of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{ncommits.pdf}
\caption{%
    \emph{Left panel}: Distribution of number of commits per committer.
    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
    package over time.
    \label{fig:ncommits}
}
\end{figure}

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
commits per contributor as of November 2017.
The relative flatness of this distribution (as demonstrated by its log-log slope of
$-0.5$) shows that the \astropypkg core package has been developed by a broad
contributor base.  A leading group of 6 developers have each added over 1000
commits to the repository, and $\sim 20$ more core contributors with at least
100 commits.
However, the distribution of contribution level (number of commits) continues
from 100 down to a single commit.
In this sense, the development of the core package has been a true community
effort and is not dominated by a single individual.
It is also important to note that the number of commits is only a rough metric
of contribution, as a single commit could be a critical fix in the package or a
fix for a typographical error.
\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
function of time since the genesis of the \astropypkg core package.
The package is still healthy: new commits are and have been contributed at a
steady rate throughout its existence.
